---
output: github_document
---

# 2021-04-30 R Learning and Development Git/GitHub practice

Today's exercise is a collection of common actions for using Git and GitHub from RStudio. The actions we will practice are:

- **Fork** a repository (make a copy of somebody else's repository on your own account). To do this you will need to [create a GitHub account](https://github.com/join) if you haven't already.
- **Clone** a repository (make a local copy of a GitHub repository on your computer so you can edit the files). Do to this you will need to [install Git](https://happygitwithr.com/install-git.html#install-git-windows) if you haven't already and make sure RStudio knows that Git exists on your system.
- **Commit** a change to one or more files in the repository.
- **Push** your changes back to GitHub. This includes [setting up RStudio to talk to GitHub](https://happygitwithr.com/credential-caching.html#how-to-get-a-pat) if you haven't already!


## Fork

In order to practice using Git/GitHub, you will need a repository to work from! You could [create a blank new repository to work with](https://github.com/new) but I think it's more exciting to start with a repo that has some content. You can use this one! To get started, click the "Fork" button at the top of this page.






```{r setup, include=FALSE}
# if not installed
# install.packages(c("ggplot2", "ggspatial", "lubridate", "rnaturalearth", "rnaturalearthdata", "sf"))
library(ggplot2)
library(ggspatial)
library(lubridate)
library(rnaturalearth)
library(rnaturalearthdata)
library(sf)

knitr::opts_chunk$set(echo = TRUE)
```

```{r}
prof_meta <- read.csv("argo_profile_meta.csv")
prof <- read.csv("argo_profiles.csv")
countries <- ne_countries(returnclass = "sf")
```

```{r argo-prof-map, message=FALSE}
ggplot(prof_meta) +
  annotation_spatial(countries) +
  shadow_spatial(
    st_bbox(
      c(xmin = -65, xmax = -35, ymin = 50, ymax = 62),
      crs = 4326
    ),
  ) +
  geom_spatial_point(aes(longitude, latitude), crs = 4326) +
  annotation_scale(location = "br") +
  coord_sf(crs = 3857) +
  theme_void()
```

```{r argo-temp, warning=FALSE}
ggplot(prof, aes(y = pres, x = temp)) +
  geom_line(
    aes(group = interaction(file, n_prof)),
    orientation = "y",
    alpha = 0.1
  ) +
  facet_wrap(vars(month(date, label = TRUE)), nrow = 3) +
  scale_y_reverse() +
  theme_bw() +
  theme(strip.background = element_blank())
```

```{r argo-psal, warning = FALSE}
ggplot(prof, aes(y = pres, x = psal)) +
  geom_line(
    aes(group = interaction(file, n_prof)),
    orientation = "y",
    alpha = 0.1
  ) +
  facet_wrap(vars(month(date, label = TRUE)), nrow = 3) +
  scale_y_reverse() +
  theme_bw() +
  theme(strip.background = element_blank())
```
